Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-17 ms.tex

\newcommand{\todo}[3]{{\color{#2} \emph{#1} TO DO: #3}}
\newcommand{\btmtodo}[1]{\todo{BEN}{red}{#1}}
\newcommand{\anytodo}[1]{\todo{ANYONE}{NavyBlue}{#1}}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci.
In this paper, we present stellar and planetary properties for all systems.
We combine archival imaging, ground-based seeing limited survey data, and
adaptive optics imaging with a detailed transit analysis scheme to confirm
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
orbital period of 33 days.
We also present \texttt{vespa}, a new general-purpose implementation
of the \citet{Morton12} procedure to calculate false positive probabilities
for \KT\ candidates.
\end{abstract}

@@

To derive the physical planet parameters conditioned on the measured stellar
parameters, we used the posterior probability distribution for quantities
measured using the light curve---from \paperit---and re-weighted them using
the results of the photometric and spectroscopic analysis.
In \paperit, the authors generated MCMC samples from the posterior
probability distribution over all the physical parameters (including stellar
mass and radius, and the planet radius) using broad, un-informative priors on
the values that are not constrained by the light curve.
As described in the Appendix, these samples can be re-weighted and used to
evaluate the posterior probability of the physical parameters of the planets
conditioned on the stellar values.
This also means that the effects of different measurements of the stellar
parameters can be easily tested by applying the method described in 
Appendix A.
The key assumption of this method is that the likelihood function used in
\paperit\ is correct.
That model was an exposure-time integrated, limb darkened light curve
\citep{Mandel02,Kipping10b} marginalized over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

@@

\appendix
\section{Computing physical planet parameters}

In \paperit, the authors generated $K$ samples from the posterior probability
distribution of the physical parameters of the systems conditioned on the
light curves using broad, un-informative priors on most of the parameters.

\begin{eqnarray}
p(w\,|\,x) &=& \frac{p(w)\,p(x\,|\,w)}{p(x)} \\
&=& \frac{q(w)\,p(x\,|\,w)}{q(x)}\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)} \\
&=& q(w\,|\,x)\,\frac{p(w)}{q(w)}\,\frac{q(x)}{p(x)}
\end{eqnarray}

We have $K$ samples
\begin{eqnarray}
w^{(k)} &\sim& p(w\,|\,x)
\end{eqnarray}
and the point of these samples is to do integrals of the form
\begin{eqnarray}
E[f(w)] &=& \int f(w)\,p(w\,|\,x) \dd w \quad.
\end{eqnarray}
Now, if we want to update this with a new measurement $p^\prime(w)$,

@@

\include{table_photometry}
%\turnpage

\include{table_stellarprops}

\include{table_planets}
\begin{turnpage}
\include{table_fpp}
\end{turnpage}

>>>>

\newcommand{\todo}[3]{{\color{#2} \emph{#1} TO DO: #3}}
\newcommand{\btmtodo}[1]{\todo{BEN}{red}{#1}}
\newcommand{\anytodo}[1]{\todo{ANYONE}{NavyBlue}{#1}}
\newcommand{\dfmtodo}[1]{\todo{DFM}{ForestGreen}{#1}}

@@

\begin{abstract}
Recently, \paperit{} presented a list of 36 planet candidates orbiting
31 stars in \KT\ \Ci.
In this paper, we present stellar and planetary properties for all systems.
We combine ground-based seeing limited survey data and
adaptive optics imaging with a detailed transit analysis scheme to confirm
\Nvalidated\ as planets and identify \Nfp\ as likely false positives.
Of particular interest is EPIC 201912552, a bright (K=8.9) M2 dwarf
hosting a \anytodo{Radius} planet with $T_{eq} = 275 \pm 15$ K and an
orbital period of 33 days.
We also present \texttt{vespa}, a new general-purpose implementation
of the \citet{Morton12} procedure to calculate false positive probabilities
for \KT\ candidates.
\end{abstract}

@@

\dfmtodo{Re-write this section.}
That model was an exposure-time integrated, limb darkened light curve
\citep{Mandel02,Kipping10b} marginalized over the parameters of the
data-driven model of the instrumental systematics described in \paperit.

@@

@@

% \begin{turnpage}
\include{table_photometry}
% \end{turnpage}
\include{table_stellarprops}
\include{table_planets}
\include{table_fpp}
